WritingSSfiles

### 2019-05-23 CreateStockSynthesis.Rmd
Get fishery stuff working

#Need to replace with interp function
wtAtAge <- data.frame(species=rep("Pacific_sardine",10),
                agecl=1:10,
                wtAtAge=c(0.0542, 0.0837,	0.1103,	0.1323,	0.1497,	0.163,	0.1729,	0.1801,	0.1854,	0.1941))
cv <- data.frame(species="Pacific_sardine", cv=c(0.2))

sardine.catch <-  create_fishery_subset(dat = results$catch,
                                         time = seq(3,495,by=5),
                                         species = species,
                                         boxes = boxes)

nyears <- 50
burnin <- 30

#Test writing CPUE in biomass
  sardine.data <- SS_write_ts(ss_data_list = sardine.data,
                ts_data = list(survObsBiom$atoutput[burnin:(burnin+nyears-1)],
                  sardine.catch.total$catch),
                CVs = c(0.2,0.2),
                data_years = list((survObsBiom$time[burnin:(burnin+nyears-1)]-3)/5+1, 
                            (sardine.catch.total$time-3)/5+1),
                sampling_month = list(rep(7,nyears),
                                      rep(1,20)),
                units = c("biomass","numbers"),
                data_type=c("CPUE","catch"),
                fleets = c(2,1))

```{r}
#Set effective sample size for age compositions
effN <- 1000
highEffN <- data.frame(species=species, effN=rep(effN, length(species)))

@@

age_comp_data

#Group age composition data by time
require(dplyr)
age_comp_proportion <- age_comp_data %>%
  group_by(time) %>%
  mutate(comp = atoutput/sum(atoutput))

#Change data format into flat structure
age_comp_proportion$id <- rep(age_bins,
                              each = nrow(age_comp_proportion)/length(age_bins))

unmelt <- dcast(data = age_comp_proportion,
                formula = time ~agecl,
                value.var = "comp")
age_comp_flat<- cbind(unmelt[order(unmelt$time),],
                      rep(effN,nrow(unmelt)))
names(age_comp_flat)[ncol(age_comp_flat)] <- "nsamp"

## Write age composition data
sardine.data <- SS_write_comps(ss_data_list = sardine.data,
               comp_matrix = list(age_comp_flat[burnin:(burnin+nyears-1),]),
               data_rows = list(sardine.data$styr:(sardine.data$styr+nyears-1)),
               sampling_month = list(rep(7,nyears)),
               data_type = c("agecomp"),
               fleet_number = c(1),
               bins = list(age_bins),
               caal_bool = c(FALSE))
sardine.data$agecomp

```{r}
# aggregate true resn per survey design
survey_aggresnstd <- aggregateDensityData(dat = results$resn,
                                          time = unique(results$nums$time),
                                          species = species,
                                          boxes = boxes)

@@

@@

len_comp_data <- ss_length_stdsurv$natlength

@@

#We want to aggregate the data by year 
caal_comp_proportion <- len_comp_data %>%
  group_by(time) %>%
  mutate(comp = round(atoutput/sum(atoutput),4)) %>%
  select(agecl, time, atoutput, lower.bins,
         upper.bins,comp)

#Use dcast to turn the data from long to wide format
unmelt_caal <- dcast(data = caal_comp_proportion,formula = time + lower.bins + upper.bins~agecl,value.var = "comp")
unmelt_caal[is.na(unmelt_caal)] <- 0

#Add nsamp column
sample_size <- apply(unmelt_caal[,(4:ncol(unmelt_caal))], FUN=sum, MARGIN=1)
caal_comp_flat<- cbind(unmelt_caal[order(unmelt_caal$time),],sample_size)
names(caal_comp_flat)[ncol(caal_comp_flat)] <- "nsamp"

#remove burnin
caal_comp_final <- filter(caal_comp_flat,
                         time %in% burnin:(burnin+nyears-1))

len_comp_proportion <- len_comp_data %>%
  group_by(time, lower.bins, upper.bins) %>%
  summarise(lencomp = sum(atoutput))

#Do the same for length composition
unmelt_len <- dcast(data = len_comp_proportion,formula = time ~lower.bins,value.var = "lencomp")
unmelt_len[is.na(unmelt_len)] <- 0

#Add over age classes to get sample size
sample_size <- apply(unmelt_len[,(2:ncol(unmelt_len))], FUN=sum, MARGIN=1)
len_comp_flat<- cbind(unmelt_len[order(unmelt_len$time),],sample_size)
names(len_comp_flat)[ncol(len_comp_flat)] <- "nsamp"

#remove burnin
len_comp_final <- filter(len_comp_flat,
                         time %in% burnin:(burnin+nyears-1))

@@

# Write CAAL and length composition data
sardine.data <- SS_write_comps(ss_data_list = sardine.data,
                               comp_matrix = list(caal_comp_final,len_comp_final),
                               data_rows = list(caal_comp_final$time,len_comp_final$time),
                               sampling_month = list(rep(7,nrow(caal_comp_final)),
               rep(7,nrow(len_comp_final))),
                               data_type = c("agecomp", "lencomp"),
                               fleet_number = c(1,1),
                               bins = list(age_bins, length_bins),
                               caal_bool = c(TRUE, FALSE))

@@

>>>>

#Set effective sample size for age compositions
effN <- 1000
highEffN <- data.frame(species=species, effN=rep(effN, length(species)))

@@

# aggregate true resn per survey design
survey_aggresnstd <- aggregateDensityData(dat = results$resn,
                                          time = unique(results$nums$time),
                                          species = species,
                                          boxes = boxes)

@@

#Need to replace with interp function
wtAtAge <- ss_length_stdsurv$muweight %>%
  select(species, agecl, time, wtAtAge = atoutput) %>%
  mutate(wtAtAge = wtAtAge/1000)

# CV function
cv <- data.frame(species="Pacific_sardine", cv=0.1)

## Catch data

```{r}
sardine.catch <-  create_fishery_subset(dat = results$catch,
                                         time = seq(1,99,by=1),
                                         species = species,
                                         boxes = boxes)

nyears <- 50
burnin <- 30
fish_years <- burnin:(burnin+nyears-1)
survey_years <- seq(3,495,by=5)[burnin:(burnin+nyears-1)]

#Test writing CPUE in biomass
  sardine.data <- SS_write_ts(ss_data_list = sardine.data,
                ts_data = list(survObsBiom$atoutput[fish_years],
                  sardine.catch.total$catch[fish_years]),
                CVs = c(0.1,0.1),
                data_years = list((survObsBiom$time[fish_years]-3)/5+1,             sardine.catch.total$time[fish_years]),
            sampling_month = list(rep(7,nyears),
                                rep(1,nyears)),
                units = c("biomass","numbers"),
                data_type=c("CPUE","catch"),
                fleets = c(2,1))

```{r}
age_comp_data

age_comp_flat <- reformat_compositions(age_comp_data,
                     round.places = 4,
                     comp_type = "agecomp")

## Write age composition data for survey
sardine.data <- SS_write_comps(ss_data_list = sardine.data,
               comp_matrix = list(age_comp_flat[burnin:(burnin+nyears-1),]),
               data_rows = list(sardine.data$styr:(sardine.data$styr+nyears-1)),
               sampling_month = list(rep(7,nyears)),
               data_type = c("agecomp"),
               fleet_number = c(1),
               bins = list(age_bins),
               caal_bool = c(FALSE))
sardine.data$agecomp

#We end up using CAAL for the survey below, so let's generate fishery age comps instead
effN <- data.frame(species="Pacific_sardine", effN=effN)

catch_numssshigh <- sample_fish(sardine.catch, effN)

#Get weights
# aggregate true resn per survey or fishery subset design
catch_aggresnss <- aggregateDensityData(dat = results$resn,
                                 time = c(0:111),
                                 species = species,
                                 boxes = boxes)

# aggregate true structn per survey or fishery subsetdesign
catch_aggstructnss <- aggregateDensityData(dat = results$structn,
                                 time = c(0:111),
                                 species = species,
                                 boxes = boxes)

#dont sample these, just aggregate them using median
catch_structnss <- sample_fish(catch_aggstructnss, effN, sample = FALSE)

catch_resnss <-  sample_fish(catch_aggresnss, effN, sample = FALSE)

str(catch_numssshigh)

catch_length <- calc_age2length(structn = catch_structnss,
                                 resn = catch_resnss,
                                 nums = catch_numssshigh,
                                 biolprm = results$biolprm, fgs = results$fgs,
                                 maxbin = 200,
                                 CVlenage = 0.1, remove.zeroes=TRUE)

@@

len_comp_data <- ss_length_stdsurv$natlength
fish_len_comp_data <- catch_length$natlength

@@

caal_comp_flat <- reformat_compositions(len_comp_data,                                round.places=4,
                comp_type="caalcomp")

#remove burnin
caal_comp_final <- filter(caal_comp_flat,
                         time %in% survey_years)

#Add over age classes to get sample size
len_comp_flat <- reformat_compositions(len_comp_data,
                                  round.places = 0,
                           comp_type="lencomp")
#remove burnin
len_comp_final <- filter(len_comp_flat,
                         time %in% survey_years)

@@

fish_len_comp_flat <- reformat_compositions(catch_length$natlength,
                                  round.places = 0,
                           comp_type="lencomp")
#remove burnin
fish_len_comp_final <- filter(fish_len_comp_flat,
                         time %in% fish_years)

fish_age_comp_flat <- reformat_compositions(catch_numssshigh,
                           comp_type="agecomp")
#remove burnin
fish_age_comp_final <- filter(fish_age_comp_flat,
                         time %in% fish_years)

comp_list <- list(caal_comp_final,len_comp_final,          fish_age_comp_final, fish_len_comp_final)

apply_month <- list(rep(7, nrow(comp_list[[1]])), rep(7, nrow(comp_list[[2]])), rep(1,nrow(comp_list[[3]])),rep(1,nrow(comp_list[[4]])))

# Write CAAL and length composition data
sardine.data <- SS_write_comps(ss_data_list = sardine.data, comp_matrix = comp_list, data_rows = list((comp_list[[1]]$time-3)/5 + 1 ,(survey_years-3)/5 + 1,fish_years,fish_years),
        sampling_month = apply_month, data_type = rep(c("agecomp", "lencomp"),2), fleet_number = c(2,2,1,1),  bins = list(age_bins, length_bins, age_bins, length_bins), caal_bool = c(TRUE, rep(FALSE,3)))

@@

## Coming up with dynamic life history parameters

Below we get the weight-length relationship parameters from atlantis, calculate h and R0 from Atlantis $\alpha$ and $\beta$ parameters, use the \code{calc_Z} function to back out natural mortality (M) from Atlantis, and use the survey length-at-age from Atlantis to estimate a growth curve.
```{r}
#Get biological parameters
biolprm <- results$biolprm
fgs <- results$fgs
li_a_use <- biolprm$wl[match(fgs$Code[match(species,fgs$Name)],biolprm$wl[, 1]), 2]/1000
li_b_use <- biolprm$wl[match(fgs$Code[match(species,fgs$Name)],biolprm$wl[, 1]), 3]
